Active Learning for Level Set Estimation

### 2013-03-25 msthpres.tex
Small fixes

\subsection*{Results}
\begin{frame}
\begin{center}
{\large Experiments}
\end{center}
\begin{enumerate}
\item \acl
\item<2-> Maximum variance sampling:
\vspace{-0.5em}
\begin{align*}
\*x_t = \argmax_{\*x\in D} \sigma_{t-1}(\*x)
\end{align*}
\item<3-> ``Straddle'' heuristic (Bryan \emph{et al.}, 2005):
\vspace{-0.5em}
\begin{align*}
\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
&\approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t = 1.96$}
\end{align*}
\end{enumerate}
\end{frame}

\begin{frame}
\begin{center}
\hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
\uncover<3>{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> Plan ahead:
\begin{itemize}
\item Select a \emph{batch} of sampling locations
\item Connect them using a Euclidean TSP path
\item Traverse path and collect measurements
\end{itemize}
\end{itemize}

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! =)
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\large Questions?\\
\vspace{2em}
\sig{\includegraphics[width=3in]{figures/dilbert}}{www.dilbert.com}
\end{center}
\end{frame}

>>>>

\subsection*{Results}
\begin{frame}
\begin{center}
{\large Experiments}
\end{center}
\begin{enumerate}
\item \acl
\item<2-> Maximum variance sampling:
\vspace{-0.5em}
\begin{align*}
\*x_t = \argmax_{\*x\in D} \sigma_{t-1}(\*x)
\end{align*}
\item<3-> ``Straddle'' heuristic (Bryan \emph{et al.}, 2005):
\vspace{-0.5em}
\begin{align*}
%\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
\*x_t \approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t^{1/2} = 1.96$}
\end{align*}
\end{enumerate}
\end{frame}

\begin{frame}
\begin{center}
\hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
\uncover<3->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> Plan ahead:
\begin{itemize}
\item Select a \emph{batch} of sampling locations (\bacl)
\item Connect them using a Euclidean TSP path
\item Traverse path and collect measurements
\end{itemize}
\end{itemize}

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\large Questions?\\
\vspace{2em}
\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
\end{center}
\end{frame}
